Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-29 bbbq_article.tex
Compare versions

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, evolutionary conservation

>>>>

{\bf Keywords:} antigen presentation, membrane proteins, adaptive immunity, transmembrane domain, epitopes, MHC-I, MHC-II, evolutionary conservation
